Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-17 nir_companions.tex
Update on Overleaf.
Fix title page

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
%\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
\title[Towards the nIR detection of BD companions]{Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere 
        under ESO programme 089.C-0977(A)}}
%\subtitle{Exploring methods to detect low mass stellar companions from blended spectra}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
  \author[J. J. Neal et. al.]{
      J. J. Neal$^{1,2}$\thanks{\email{jason.neal@astro.up.pt}}
     P. Figueira$^{3,1}$ 
 N. C. Santos$^{1,2}$
    C. Melo$^{3}$
\\
% List of institutions
$^{1}$Instituto de Astrof\'{\i}sica e Ci\^encias do Espa\c{c}o, CAUP, Universidade do Porto, Rua das Estrelas, PT4150-762 Porto, Portugal
$^{2}$Departamento de F\'{\i}sica e Astronomia, Faculdade de Ci\^{e}ncias, Universidade do Porto, Portugal
$^{3}$European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
}

@@

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
%\maketitle

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
%\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
\title[Towards the nIR detection of BD companions]{Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}}
%\subtitle{Exploring methods to detect low mass stellar companions from blended spectra}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor

 \author[J. J. Neal et al.]{
  J. J. Neal$^{1,2}$\thanks{E-mail: jason.neal@astro.up.pt}
  P. Figueira$^{3,1}$ 
 N. C. Santos$^{1,2}$
 C. Melo$^{3}$
 \\
 % List of institutions
 $^{1}$Instituto de Astrof\'{\i}sica e Ci\^encias do Espa\c{c}o, CAUP, Universidade do Porto, Rua das Estrelas, PT4150-762 Porto, Portuga\\l
 $^{2}$Departamento de F\'{\i}sica e Astronomia, Faculdade de Ci\^{e}ncias, Universidade do Porto, Portugal\\
 $^{3}$European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile\\
}

@@

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
